\documentclass[usenames,dvipsnames,aspectratio=169]{beamer}
\usepackage[utf8]{inputenc}
\usecolortheme{seahorse}
\usepackage{enumitem,amsmath,xfrac,dsfont,amsfonts,bbm,cancel,euler,ulem}
\usepackage{apacite,natbib}
\usepackage{hyperref}
\usepackage{caption,subcaption,booktabs,multicol,adjustbox}
\usepackage{xcolor}


\title{The Industrial Revolution in Services  \small{Applied Macroeconomics: Micro Data for Macro Models} }
\author{Author: Chang-Tai Hsieh \and Esteban Rossi-Hansberg \\ Presented by: Jose M. Quintero}



\AtBeginSection[]
{
  \begin{frame}<beamer>
    \frametitle{Outline}
    \tableofcontents[currentsection]
  \end{frame}
}

\AtBeginSubsection[]
{
   \begin{frame}
        \frametitle{Outline}
        \tableofcontents[currentsubsection]
   \end{frame}
}



\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Good Stuff - B52's}
\begin{itemize}[label=\textcolor{teal}{$\blacktriangleright$}]
    \item The facts
    \begin{enumerate}[label=\textbf{\textcolor{teal}{\arabic*.}}]
        \item Explore a very rich variation in the data
        \item Tell a compelling story
    \end{enumerate}
    \vfill
    \item The model
    \begin{enumerate}[label=\textbf{\textcolor{teal}{\arabic*.}}]
        \item Tractable where the margins of adjustment are very clear
        \item Decomposition of mark-up increase over time. 
    \end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}{Bad Habits - Ed Sheeran}
     \begin{itemize}[label=\textcolor{teal}{$\blacktriangleright$}]
         \item Exposition: Though the facts are clear, how they are presented could be improved. Ej. Table 5 is perfect for a graph
         \vfill
         \item Model: Everything is efficient
     \end{itemize}
\end{frame}

\begin{frame}{New - Paul McCartney} 
    \begin{itemize}[label=\textcolor{teal}{$\blacktriangleright$}]
        \item How do we endogenize technological change? 
        \item How are the dynamics? Transition to a new equilibrium? 
    \end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{Homework}
\begin{enumerate}[label=\textbf{\textcolor{teal}{(\arabic*)}},leftmargin=*]
    \item Assume CES across industries with elasticity $\rho>0$. Does employment rising in an industry mean its TFP must have risen relative to other industries?
    \item[\textbf{\textcolor{teal}{(S)}}] Not necessarily. It depends on the complementarity/substitability of industries. If $\rho>1$ then yes.  
    \item Suppose there are non-homothetic preferences across industries, with services a luxury and (manufactured) goods a necessity. Does employment rising in services mean its TFP must have risen relative to other industries?
    \item[\textbf{\textcolor{teal}{(S)}}] Not really. Any kind of shock other than TFP that yields an increase in wages or decrease in prices would imply an in consumption of luxury goods due to the 
    \item Labour share has fallen in manufacturing but not so much outside manufacturing. Is the flat labor share in services consistent with the model in this paper?
    \item[\textbf{\textcolor{teal}{(S)}}] It will require some reinterpretation to make the history consistent, and additional assumptions such as fix cost have stayed constant. But the model could have a twist to accommodate the history,  
\end{enumerate}

\end{frame}

\end{document}

